\plaintitle

### 2025-05-20 docs/style/article-body.tex
fixed most small comments from meeting

In computer science, there are many applications for randomly generated numbers. From generating keys for cryptography, salting password hashes, load balancing in distributed systems, memory addressing and so much more. However, the process of producing these random numbers tends to be pseudo-random, e.g.~utilizing the current states of various modules \cite{randomness}. These numbers do not generate true randomness, and in order to heighten security other methods of generating these are required. Current random number generators (\emph{RNG}) are usually implemented in code, using certain states of the host machine as a starting point before running a predetermined algorithm \cite{randomness}. This pseudo-random number generation (\emph{PRNG}) comes with the drawback that the result is always deterministic, provided that the initial state is known.

@@

True random numbers, then, cannot be produced solely through code. These systems require some input that is neither replicable nor reproducible. One method that can be realistically used is the inherently random movement of lava lamps \cite{lavarand}, which is used as a backup source of randomness for Cloudflare\footnote{\href{https://blog.cloudflare.com/randomness-101-lavarand-in-production/}{Cloudflare.com, accessed 2025-03-10}}. Another proposed solution for this is quantum random number generation (\emph{QRNG}) \cite{QRNG}. By reading quantum fluctuation signals from any given source, for instance an optical signal, the inherent natural unpredictability of said signal can be harnessed in order to produce a random number from a state that is nigh impossible to reproduce accurately.

Further details about how this signal is produced and sampled will be introduced in section 2 and 3, and builds on the work of Clason \cite{Clason2023}. This optical signal needs to be converted to a stream of random, raw bits via an Analog to Digital Converter (\emph{ADC}). Some processing of the data has to be done in order to ensure that the data is workable and to remove potential deterministic patterns from these random bits. One method for this post-processing we will explore in this work is Toeplitz extraction \cite{toeplitz}, typically performed on the host computer utilizing the randomly generated numbers. While this system could very well be implemented on physically larger hardware, thus avoiding the constraints that limited hardware introduces, Clason proposes a simpler and cheaper way to achieve QRNG \cite{Clason2023}. In keeping with this, utilizing microcontrollers rather than a host computer for processing the raw bits extracted further helps to keep the costs low and the solution reasonably complex. Additionally, this allows the system to be self-contained, for instance a simple and portable USB-device which both generates and processes true random numbers. Further details regarding the microcontrollers used in our work will be outlined in section 3.

@@

@@

>>>>

In computer science, there are many applications for randomly generated numbers. From generating keys for cryptography, salting password hashes, load balancing in distributed systems, memory addressing and so much more. However, the process of producing these random numbers tends to be pseudo-random, e.g.~utilizing the current states of various modules \cite{randomness}. Pseudo-random numbers do not generate true randomness, and in order to heighten security, other methods of generating random numbers are required. Current random number generators (\emph{RNG}) are usually implemented in computer programs, using certain states of the host machine as a starting point before running a predetermined algorithm \cite{randomness}. This pseudo-random number generation (\emph{PRNG}) comes with the drawback that the result is always deterministic, provided that the initial state is known.

@@

True random numbers, then, cannot be produced solely through code. These systems require some input that is neither replicable nor reproducible. One method that can be realistically used is the inherently random movement of lava lamps \cite{lavarand}, which is used as a backup source of randomness for Cloudflare\footnote{\href{https://blog.cloudflare.com/randomness-101-lavarand-in-production/}{Cloudflare.com, accessed 2025-03-10}}. Another proposed solution for this is quantum random number generation (\emph{QRNG}) \cite{QRNG}. By reading quantum fluctuation signals from any given source, for instance an optical signal, the inherent natural unpredictability of said signal can be harnessed in order to produce a random number from a state that is nigh impossible to reproduce accurately. Clason \cite{Clason2023} presents a device that generates a fluctuating analogue signal utilizing this method, which we will use as a basis for our work.

Further details about how this signal is produced and sampled will be introduced in section 2 and 3. The optical signal output by the device described in \cite{Clason2023} needs to be converted to a stream of random, raw bits via an Analog to Digital Converter (\emph{ADC}). Some post-processing of the said raw bits has to be performed in order to ensure that the bits are workable, and to remove potential deterministic patterns from the data. One method for this post-processing we will explore in this work is Toeplitz extraction \cite{toeplitz}, typically performed on the host computer utilizing the randomly generated numbers.

\[
    \text{OQRNG Analogue output} \rightarrow \text{ADC-converter} \rightarrow \text{post-processing}
\]

Clason proposes a simpler and cheaper way to achieve QRNG \cite{Clason2023}. In keeping with this, utilizing microcontrollers rather than a host computer for processing the raw bits extracted further helps to keep the costs low and the solution reasonably complex. Additionally, this allows the system to be self-contained, for instance a simple and portable USB-device which both generates and processes true random numbers. Further details regarding the microcontrollers used in our work will be outlined in section 3.

@@

\subsection{7 CONCLUSION}\label{conclusion}

@@

2025-05-20: Unfortunately, we've missed adding concrete details about changes made up until this point. Fix later.
